Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-02-17 tex/VHzQ.tex
further VHzQ.tex update

WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m. The all sky `ALLWISE' catalogue release, contains nearly 750 million detections at high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}, of which over 4.5M AGN candidates have been identified with 90\% reliability \citep{Assef2018}.  \citet{Blain2013} presented WISE mid-infrared (MIR) detections of 17 (55\%) of the then known 31 quasars at $z > 6$. However, \citet{Blain2013} was compiled with the WISE `All-Sky' data release, as opposed to the superior AllWISE catalogues. That sample only examined the 31 known $z>6$ quasars; our sample has 170 objects with redshift $z \geq 6.00$, with $xyz$ detected in WISE {\bf NPR to double check!!'}. \citet{Banados2016} reports WISE W1, W2, W3 and W4 magnitudes for the Panoramic Survey Telescope and Rapid Response System 1 \citep[Pan-STARRS1, PS1;][]{Kaiser2002, Kaiser2010}, but with no further investigation into the reddest WISE waveband for the VH$z$Qs.

@@

Here we present for the first time the combined near-infrared properites (from UKIRT and VIRCAM) and the new mid-infrared unWISE for all the spectroscopically known $z\geq5.00$ quasars. Our motivations are numerous and include: {\it (i)} establishing the first complete catalogue of $z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry available for the quasars; {\it (iii)} making the first study of near- and mid-IR variability of the VHzQ population and {\it (iv)} establishing the photometric properties for upcoming surveys and telescopes including the Large Synoptic Survey Telescope (LSST)\footnote{\href{https://www.lsst.org}{{lsst.org}}}, ESA {\it Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}} and the {\it James Webb Space Telescope} (JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}. We chose redshift $z=5.00$ as our lower redshift limit due to a combination of garnishing a large sample, adequately spanning physical properties (e.g. luminosity, age of the Universe) and to highlight the parts of $L-z$ parameter space where $z>5$ quasars are still wait to be discovered.

@@

Most of these objects are easily identified by their broad Ly$\alpha$ emission line, \nv emission and characteristic shape blueward of 1215\AA\ in the rest-frame. As we shall see, some of the recently discovered objects are close to the galaxy luminosity function characteristic luminosity $M^{*}$, and some have relatively weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures 7 and 10 in][]{Banados2016}. We leave aside detailed investigation and discussion into spectral features and line strengths, and take as given the published spectra and reshift identifications.

The breakdown of how many VH$z$Q each survey reports is given in
Table~\ref{tab:surveys}. We assume the reader is familiar with the
Sloan Digital Sky Survey (SDSS) and the Pan-STARRS1 (PS1; PSO in
Table~\ref{tab:surveys}.  ) survey and these surveys alone identified
over half (54.6\%) of the VH$z$Q population. Data from the
Hyper Suprime-Cam (HSC) on the Subaru telecope is responsible for
13.6\% of our dataset (HSC+SHELLQs in Table~\ref{tab:surveys}). The
combination of surveys is also vital for identifying VH$z$Qs. The
UKIDSS Large Area Survey (ULAS) on its own, or in combination with
other surveys is responsible for 6.5\% of the sample (SUV+ULAS)
including the highest-$z$ object. Where more than one survey is used
for the high-redshift identification (e.g. via shorter-band veto and
longer wavelength detection) we follow the discovery paper naming
convention.

@@

\section{A. Photometric Bands and Conversions}
    Due to the differing normalizations between the
    SDSS and  UKIDSS photometric systems, certain corrections are required.  To present
    our data in the  purest sense, all the NIR magnitudes from UKIDSS
    (originally AB magnitudes)  were corrected to Vega magnitudes as
    suggested in \citet{Hewett2006}.

>>>>

WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m. The all sky `ALLWISE' catalogue release, contains nearly 750 million detections at high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}, of which over 4.5M AGN candidates have been identified with 90\% reliability \citep{Assef2018}.  \citet{Blain2013} presented WISE mid-infrared (MIR) detections of 17 (55\%) of the then known 31 quasars at $z > 6$. However, \citet{Blain2013} was compiled with the WISE `All-Sky' data release, as opposed to the superior AllWISE catalogues. That sample only examined the 31 known $z>6$ quasars; our sample has 170 objects with redshift $z \geq 6.00$ (with $x$ detected in WISE {\bf NPR to double check!!}). \citet{Banados2016} reports WISE W1, W2, W3 and W4 magnitudes for the Panoramic Survey Telescope and Rapid Response System 1 \citep[Pan-STARRS1, PS1;][]{Kaiser2002, Kaiser2010}, but with no further investigation into the reddest WISE waveband for the VH$z$Qs.

@@

Here we present for the first time the combined near-infrared properites (from UKIRT and VIRCAM) and the new mid-infrared unWISE for all the spectroscopically known $z\geq5.00$ quasars. Our motivations are numerous and include: {\it (i)} establishing the first complete catalogue of $z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry available for the quasars; {\it (iii)} making the first study of near- and mid-IR variability of the VHzQ population and {\it (iv)} establishing the photometric properties for upcoming surveys and telescopes including the Large Synoptic Survey Telescope (LSST)\footnote{\href{https://www.lsst.org}{{lsst.org}}}, ESA {\it Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}} and the {\it James Webb Space Telescope} (JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}. We chose redshift $z=5.00$ as our lower redshift limit due to a combination of garnishing a large sample, adequately spanning physical properties (e.g. luminosity, age of the Universe) and to highlight the parts of $L-z$ parameter space where $z>5$ quasars still wait to be discovered.

@@

Most of these objects are easily identified by their broad Ly$\alpha$
emission line, \nv emission and characteristic shape blueward of
1215\AA\ in the rest-frame. As we shall see, some of the recently
discovered objects are close to the galaxy luminosity function
characteristic luminosity $M^{*}$, and some have relatively weak or
maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures 7 and 10
in][]{Banados2016}. We leave aside detailed investigation and
discussion into spectral features and line strengths, and take as
given the published spectra and redshift identifications.

The breakdown of how many VH$z$Q each survey reports is given in Table~\ref{tab:surveys}. The Sloan Digital Sky Survey (SDSS) and the Pan-STARRS1 (PS1; PSO in Table~\ref{tab:surveys}) survey and alone identified over half (54.6\%) of the VH$z$Q population. Data from the Hyper Suprime-Cam (HSC) on the Subaru telecope is responsible for 13.6\% of our dataset (HSC+SHELLQs in Table~\ref{tab:surveys}). The combination of surveys is also vital for identifying VH$z$Qs. The UKIDSS Large Area Survey (ULAS) on its own, or in combination with other surveys is responsible for 6.5\% of the sample (SUV+ULAS) including the highest-$z$ object. Where more than one survey is used for the high-redshift identification (e.g. via shorter-band veto and longer wavelength detection) we follow the discovery paper naming convention.

@@

\section{A. Photometric Bands and Conversions}\label{sec:filters} 
    Due to the differing normalizations between the
    SDSS and  UKIDSS photometric systems, certain corrections are required.  To present
    our data in the  purest sense, all the NIR magnitudes from UKIDSS
    (originally AB magnitudes)  were corrected to Vega magnitudes as
    suggested in \citet{Hewett2006}.
